---
title: "Assignment 6"
author: "Dagmar Heintze"
---

```{r}
library(haven) 
TEDS_2016 <- read_stata("https://github.com/datageneration/home/blob/master/DataProgramming/data/TEDS_2016.dta?raw=true")
```

 Are female voters more likely to vote for President Tsai? Why or why not? 

```{r}
glm.vt=glm(votetsai~female, data=TEDS_2016,family=binomial)
summary(glm.vt)
```

Females are not more likely to vote for president Tsai. A voter being femae leads to a decrease in likelihood of them voring for the president. To assess the why or why not question, I need to further assess the data.

```{r}
plot(glm.vt)
```

```{r}

glm_v1 <- glm(formula = votetsai ~ female + KMT, family = binomial, data = TEDS_2016)
summary(glm_v1)
```

```{r}
glm_v2 <- glm(formula = votetsai ~ female + DPP, family = binomial, data = TEDS_2016)
summary(glm_v2)
```

```{r}

```

```{r}
glm_v4 <- glm(formula = votetsai ~ female + DPP + age + edu, family = binomial, data = TEDS_2016)
summary(glm_v4)
```

```{r}
glm_v5 <- glm(formula = votetsai ~ female + DPP + age + edu + income, family = binomial, data = TEDS_2016)
summary(glm_v5)
```

```{r}
glm_v6 <- glm(formula = votetsai ~ female + KMT + age + edu + income, family = binomial, data = TEDS_2016)
summary(glm_v6)
```

I find that DPP membership is the single strongest predictor for voting for president Tsai. All other variables, a voter being female, a higher level of education, income and a higher age all lead to a decrease in likelihood of voting for the president. Membership in the KMT party, furthermore, has a strong, negative and significant effect on the likelihood of a person voting for president Tsai.

```{r}
glm_model2 <- glm(formula = votetsai ~ Independence + Econ_worse + Govt_dont_care + Minnan_father + Mainland_father + Taiwanese, family = binomial, data = TEDS_2016)
summary(glm_model2)
```

```{r}
glm_model3 <- glm(formula = votetsai ~ DPP + Independence + Econ_worse + Govt_dont_care + Minnan_father + Mainland_father + Taiwanese, family = binomial, data = TEDS_2016)
summary(glm_model3)
```

When testing two alternative model specifications, I find that DPP membership is still a strong and statistically significant predictor for voting for president Tsai. Furthermore, support for Taiwan's independence, a negative view of the economy, and a person self-identifying as Taiwanese are all positive and statistically significant predictors for a voter electing the president. A voter being a descendant from mainland China is a negative and statistically significant predictor for voting for president Tsai.
