# [[Load the Data:]{.underline}]{.smallcaps}

```{r}
library(haven)
TEDS_2016 <- read_stata("https://github.com/datageneration/home/blob/master/DataProgramming/data/TEDS_2016.dta?raw=true")

View(TEDS_2016)

```

# [[Remove observations with any missing values]{.underline}]{.smallcaps}

```{r}
TEDS_2016_clean <- na.omit(TEDS_2016)
```

# [[Descriptive Statistics]{.underline}]{.smallcaps}

```{r}
summary(TEDS_2016_clean) # Summary statistics for all variables # If you want to see summary statistics for specific variables, you can specify them: summary(TEDS_2016_clean[c("Tondu", "age", "income", "edu")])
```

# [[Correlation Analysis]{.underline}]{.smallcaps}

```{r}
correlation_matrix <- cor(TEDS_2016_clean[c("Tondu", "age", "income", "edu")])
correlation_matrix 

```

# [[Scatter plots]{.underline}]{.smallcaps}

```{r}
plot(TEDS_2016_clean$age, TEDS_2016_clean$Tondu, xlab = "Age", ylab = "Tondu", main = "Scatter plot of Age vs. Tondu")
```

# [[Box plots]{.underline}]{.smallcaps}

```{r}
boxplot(Tondu ~ female, data = TEDS_2016_clean, xlab = "Female", ylab = "Tondu", main = "Box plot of Tondu by Gender")
```

# [[Histograms/Density plots]{.underline}]{.smallcaps}

```{r}
hist(TEDS_2016_clean$Tondu, xlab = "Tondu", main = "Histogram of Tondu") 
```

# [[Linear Regression (assuming Tondu is continuous)]{.underline}]{.smallcaps}

```{r}
lm_model <- lm(Tondu ~ age + income + edu, data = TEDS_2016_clean)
summary(lm_model)

```

```{r}

unique(TEDS_2016_clean$Tondu)
# Convert Tondu to factor 
TEDS_2016_clean$Tondu <- factor(TEDS_2016_clean$Tondu)

# Recode Tondu based on the levels
TEDS_2016_clean$Tondu <- ifelse(TEDS_2016_clean$Tondu == "Status quo", 0,
                                ifelse(TEDS_2016_clean$Tondu == "Independence now", 1, NA))

class(TEDS_2016_clean$Tondu)

```

```         
```

# [[Rerun the analysis for the votetsai variable]{.underline}]{.smallcaps}

# [[Descriptive Statistics]{.underline}]{.smallcaps}

```{r}
summary(TEDS_2016_clean$votetsai)

```

# [[Correlation Analysis]{.underline}]{.smallcaps}

```{r}
correlation_matrix_votetsai <- cor(TEDS_2016_clean[c("votetsai", "age", "income", "edu")])
print(correlation_matrix_votetsai)

```

# [[Regression Analysis: Linear Regression:]{.underline}]{.smallcaps}

```{r}
lm_model_votetsai <- lm(votetsai ~ age + income + edu, data = TEDS_2016_clean)
summary(lm_model_votetsai)

```

# [[Logistic Regression:]{.underline}]{.smallcaps}

```{r}
logit_model_votetsai <- glm(votetsai ~ age + income + edu, data = TEDS_2016_clean, family = binomial)
summary(logit_model_votetsai)

```

# [[Generate A Frequency Table:]{.underline}]{.smallcaps}

```{r}
# Assigning labels to the Tondu variable
TEDS_2016$Tondu <- factor(TEDS_2016$Tondu, labels = c("Unification now", "Status quo, unif. in future", "Status quo, decide later", "Status quo forever", "Status quo, indep. in future", "Independence now", "No response"))

# Generating frequency table
frequency_table <- table(TEDS_2016$Tondu)
print(frequency_table)

# Generating barchart
barplot(frequency_table, main = "Frequency of Tondu Responses", xlab = "Tondu", ylab = "Frequency")

```
